\subsection{Champagne Prototyping}\label{sec:cham-app}
In this section we analyse the video files from the usability experiment using the champagne prototyping methodology. This method uses two different analysis strategies; attention investment and cognitive dimensions. In both of these analyses we count mentions of each feature or dimension. We present these using bullets in tables, which is recommended by \cite{blackwell2004champagne}. A closed bullet (\mn) means that a participant mentioned an aspect of the feature, when the participant mentioned it multiple times an open bullet is used (\mns). The categories, \textit{Correct \& Unprompted} and \textit{Correct \& Prompted} are instances where the participants mention or explain a feature correctly and/or positively. The last category are instances where features are mentioned negatively, incorrectly or is a cause for confusion.

\input{chapters/04-usability/attention-investment.tex}

\subsection{Cognitive Dimensions}\label{sec:cog-dim-app}
In this section we use the cognitive dimensions framework to aid the analysis of the video from the usability test. In this analysis we count the number of times the participants experience or mention problems with each dimension. We use the same notation that was presented in the previous section. The frequency of mentions can be seen in \tableref{cog-dim-findings}. The mentions counted are any instances where the participants said or did some thing that fit under a cognitive dimension. Many of the counted instances are therefore not explicit statements made by the participants, but rather instances where their actions fell under one of the categories.%Furthermore, the mentions are not necessarily negative, but might also reflect instances where the user made use of the given dimension.

\makeTable{
	{| l | l | l |}
	\hline
	\textbf{Dimension} & \textbf{F\#} & \textbf{C\#} \rowEnd
	Abstract Gradient & \mn & \mn \rowEnd
	Closeness of Mapping & \mn\mn &  \rowEnd
	Consistency & \mn\mn\mns\mns\mns & \mn\mn \rowEnd
	Diffuseness/Terseness & \mn\mn\mns & \mn \rowEnd
	Error-proneness & \mn\mns\mns\mns\mns & \mn\mn \rowEnd
	Hard Mental Operations & \mn\mn\mns & \mns \rowEnd
	Hidden Dependencies & \mn\mn & \mn \rowEnd
	Premature Commitment & \mn\mn\mn & \rowEnd
	Progressive Evaluation & \mn\mn\mns & \mn\mn \rowEnd
	Role-expressiveness & \mn\mn\mns\mn & \mn\mn \rowEnd
	Secondary Notation and Escape from Formalism & & \rowEnd
	Viscosity & \mn & \mn \rowEnd
	Visibility and Juxtaposability & \mn\mns & \mn \rowEnd
}{Cognitive Dimensions Findings}{cog-dim-findings}

It is not surprising that participants encountered more problems with \fs than they did with \cs. Participants were selected based on the criteria stated in \secref{par-crit}, these included requirements for \cs experience and limited to no  \fs experience. This allowed us to study the potential adoption difficulties of \fs. The higher frequency of mentions when using \fs is inline with this.

While an overview can be gained from \tableref{cog-dim-findings}, it does not provide adequate information of \textit{why} a participant would undertake a certain strategy or action. Therefore, selected instances among the mentions, are analysed further in the following sections.

\subsection{Instance Analysis}
Some instances during the test made the difficulties of using \fs and the functional paradigm more clear than others. In this section, these instances are explored and examined in order to discover the problems faced by developers adopting \fs in a gameplay programming setting.% Each instance is discussed and explored under the dimension it belongs to.

\input{chapters/04-usability/dimensions/consistency.tex}
\input{chapters/04-usability/dimensions/role-expressiveness.tex}
\input{chapters/04-usability/dimensions/secondary-notation.tex}
\input{chapters/04-usability/dimensions/viscosity.tex}
