\subsection{Results Analysis} \label{sec:test-results}
The result of the tests was six git branches with source code written by the participants along with five video-files. Sadly the video-recording program broke down during one of the tests and we were unable to recover the file. We took notes during the tests and will refer to those instead. Whenever we quote the notes rather than the participant, we will clearly indicate that.

In general the participants were able to complete roughly one test case, some didn't and some started the second as well. This was the case for both \fsh and \csh. \tableref{participant:exercises} lists the participants and which exercises they were assigned. Please note that participant four was assigned the Dialogue Tree task, but asked for another task as he found it too hard.

\makeTable{
	{| l | p{0.35\textwidth} | p{0.35\textwidth} |}
	\hline
	\textbf{Participant} & \textbf{F\#} & \textbf{C\#} \rowEnd
	1 & \gls{FiPS} Controller & 3rd Person Controller \rowEnd
	2 & Magnetism & Unit Management \rowEnd
	3 & Armour Graph & Talent Tree \rowEnd
	4 & Dialogue (skipped as it was too hard), \gls{FiPS} & 3rd Person Controller \rowEnd
	5 & Magnetism & Unit Management, Currency \rowEnd
	6 & Dialogue & Currency \rowEnd
}{Participants and their assigned tasks in F\# and C\#}{participant:exercises}

\subsubsection{Questionnaire}
All participants were asked to estimate their own skill levels in these categories and give a ballpark estimate of how many Unity applications they had developed. The results can be seen in \tableref{participant-scores}.

\makeTable{
	{| c | r | r | r | r | r |}
	\hline
	\textbf{Participant}&\textbf{\csh}&\textbf{Unity}&\textbf{Game Dev}&\textbf{Functional}&\textbf{Unity Apps} \rowEnd
	1 & 9 & 9 & 5 & 3 & 25 \rowEnd
	2 & 8 & 8 & 7 & 2 & 10 \rowEnd
	3 & 8 & 8 & 2 & 1 & 12 \rowEnd
	4 & 10 & 10 & 8 & 1 & 10 \rowEnd
	5 & 9 & 9 & 9 & 2 & 10 \rowEnd
	6 & 8 & 8 & 9 & 6 & 5 \rowEnd
}{Participants Self Evaluations}{participant-scores}

\newcommand{\mn}{\newmoon}
\newcommand{\mns}{\fullmoon}

\subsubsection{Data Processing}
In the following section we will process the data from the tests, using methodology presented in \secref{prog-usability}. The tests were constructed using the Champagne Prototyping methodology and the analysis of the data will also follow this approach. Champagne Prototyping uses two methodologies for data processing; Attention Investment Model and Cognitive Dimensions.

\input{chapters/04-usability/syntax.tex}
\input{chapters/04-usability/champagne.tex}

%Asger: "Nu copy-paster jeg kode. Det er ikke godt, men det er spiludvikling." - 56:15
%Asger: "Det er det jeg godt kan lide ved funktionelt: De tvinger dig til at gøre det pænt, men her har jeg lov til at svine." -59:10
%Participant 3: "Altså hvis det er noget jeg skal bruge tre gange, så er det måske... altså så er det fint nok bare lige at kopiere det, men eller kunne man godt lige lave en funktion." - 13:45