\chapter{Usability Evaluation}
In this chapter we research usability of functional-style programming in gameplay programming. We first use the cognitive dimensions framework to discuss our experience with the transition from C\# to F\# and compare the two languages.

Afterwards we conduct a usability test of \fs in Unity. The tests are formulated based on the \champagne methodology (see \secref{champagne}). For this test the Unity game engine was extended, via a plugin to support programming in \fs\cite{fsharp2019plugin}. In addition, a \gls{FRP} module was implemented in \fs for Unity. These two extensions served as the prototype under test.% The test cases in the following section were formulated as the experimental tasks. Finally a number of domain experts, in this case experienced Unity developers, were selected as participants.

The usability test was intended to examine the viability of using functional programming in commercial game engines. Again, we drew on the approaches presented by the game development gurus; Carmack and Sweeney. Carmack's opinion of using functional-style programming whenever convenient is represented by \cs, which has many functional-style constructs. Sweeney's opinion of a pure functional language with explicit effects typing constructs is (somewhat) represented by \fs. \fs is pure by default, but it has the \ttt{mutable} keyword, which allows the programmer to declare mutable variables. F\# does not support effects typing, but the use of the \m{mutable} keyword along with the \ttt{\textless-} operator forces programmers to think about mutability. We argue that this presents and \dquote{soft} introduction to the act of effects typing.

\input{chapters/04-usability/cognitive-dimensions.tex}
\section{Usability Evaluation}
In this section we present the usability evaluation that was conducted as part of the project. We first go over the setup of the test, presenting participant selection criteria and describe the tasks that were given to the participants. We then turn to the results of the test, where we adopt the analysis method described in \champagne\cite{blackwell2004champagne}. The \champagne method yields rather shallow analysis results and hence we present a more in-depth analysis of the problems using the \cognitive framework. Finally we discuss potential sources of errors of the experiment.

\input{chapters/04-usability/setup.tex}
\input{chapters/04-usability/results.tex}
\input{chapters/04-usability/validity.tex}
