\subsubsection{Abstract Gradient}\label{sec:our-abstract-gradient}
The abstract gradient is measured from abstraction hating, through abstraction tolerant, to abstraction loving. The abstractions measured are the notations' ability to group elements and refer to them as a single entity. Most modern textual-programming languages make extensive use of abstraction and functional languages even more so\cite{hudak1989conception}. \fs is a functional-programming language with object-oriented features allowing for extensive abstractions.

On the other hand \cs is an object-oriented language which supports functional features. This means that \cs also supports extensive abstraction. The main difference lies in the fact that \cs is object-oriented programming first and \fs is functional programming first. %Functional programming tends to make use of abstraction more frequently, however that does not mean that other paradigms do not use abstraction\needcite.
Considering the high level of abstraction in both languages they will both be considered abstraction loving in this report. \cite{bendersky:abstraction} presents a discussion, underlining that functional languages generally rely on function abstraction, treating types as thin data containers, whereas object oriented languages rely on data abstraction, where functionality is associated with the types. The author notes that this may surface as making it harder to add new types in functional languages and adding functionality in object-oriented languages. A similar orthogonality is also expressed in two out of three of Tennent's language design principles\cite{tennent1977language}, namely the principle of abstraction and the principle of data type completeness.
