\subsection{Champagne Prototyping}
In this section we analyse the video files from the usability experiment using the champagne prototyping. This method uses two different analysis strategies; attention investment and cognitive dimensions. In both of these analyses we count mentions of each feature. We present these counts using bullets in tables, which is recommended by \cite{blackwell2004champagne}. A closed bullet (\mn) means that a participant mentioned an aspect of the feature, when the participant mentioned it multiple times an open bullet is used (\mns). The categories, \textit{Correct \& Unprompted} and \textit{Correct \& Prompted} are instances where the participants mention or explain a feature correctly and/or positively. The last category are instances where features are mentioned negatively, incorrectly or is a cause for confusion.

\input{chapters/05-usability/attention-investment.tex}

\subsubsection{Cognitive Dimensions}
\subsection{Cognitive Dimensions}
In this section we use the cognitive dimensions framework to aid the analysis of the video from the usability test. In this analysis we count the number of times the participants experience or mention problems with each dimension. We use the same notation that was presented in the previous section.

\begin{table}[H]
	\alignCenter{
	\begin{tabular}{| l | c |}\hline
		& \textbf{F\#} & \textbf{C\#} \rowEnd
	 	Abstract Gradient &  \rowEnd
		Closeness of Mapping &  \rowEnd
		Consistency &  \rowEnd
		Diffuseness/Terseness &  \rowEnd
		Error-proneness & \rowEnd
		Hard Mental Operations &  \rowEnd
		Hidden Dependencies &  \rowEnd
		Premature Commitment &  \rowEnd
		Progressive Evaluation &  \rowEnd
		Role-expressiveness &  \rowEnd
		Secondary Notation and Escape from Formalism &  \rowEnd
		Viscosity & \rowEnd
		Visibility and Juxtaposability & \rowEnd
	\end{tabular}}
	\caption{Cognitive Dimensions Findings}
	\label{tab:cog-dim-findings}
\end{table}

\subsection{Analysis}
\metasheep

\input{chapters/05-usability/dimensions/consistency.tex}
\input{chapters/05-usability/dimensions/secondary-notation.tex}
\input{chapters/05-usability/dimensions/viscosity.tex}
