\subsubsection{Consistency}\label{sec:part-cons} % p6 20:15
All participants had prior \cs experience which affected their expectations. This was apparent when participants applied \cs methodology in the \fs code. An example of this is the confusion of types some participants experienced. Several participants noted that they preferred strict typing or specifying types manually. An example of this can be seen in \lstref{type-conf}.

\begin{listing}[H]
\begin{minted}{fsharp}
[<SerializeField>]
let mutable _velocity = 5.0f
[...]
member this.HandleMoveForward() =
  this.transform.position+=new Vector3(0,0,this._velocity)
\end{minted}
\caption{Problem experienced with types in F\#. The \m{Vector3} constructor accepts \m{float}s and are invoked with \m{int}-parameters.}
\label{lst:type-conf}
\end{listing}

In \lstref{type-conf} the participant correctly types the \ttt{\_velocity} variable on line 2. However, when attempting to set the object's position on line 5, the participant first uses \ttt{0} instead of \ttt{0.0f}. This valid in \cs, but not in \fs. This is an instance of confusion surrounding the automatic type inference of variables and the typing of literals.

\begin{listing}[H]
\begin{minted}{fsharp}
let moveMagneticBalls (objs:GameObject[]) (center:GameObject) =
  objs center |> Array.map (fun i ->
    i.transform.LookAt(center.transform)
    i.transform.Translate(i.transform.forward * Time.deltaTime * speed))
\end{minted}
\caption{Closure misunderstanding. The user attempts to catch \m{center} in the closure by piping it into the map-function.}
\label{lst:clos-mis}
\end{listing}

Some participants also experienced issues with closures. In \lstref{clos-mis} a participant has defined a function to move a number of objects towards a center point. The center point, \ttt{center}, is passed as a parameter, but the participant became confused as to how to pass it to the lambda expression. Therefore center was added on line 2 after \ttt{objs} and piped into the \ttt{map} function. This causes an error because \ttt{objs center} is now a function invocation to a non-existent function, \ttt{objs}, with the argument \ttt{center}. Passing \ttt{center} to the lambda function is unnecessary, because it is captured in the lambda's closure.

The behaviour described is consistent within \fs, but not with the expectations of the participant. Arguably, this instance is a product of the participant's inexperience with functional programming, however it is an example of the disharmony between the largely consistent rules of \fs and the expectations of programmers. These consistency issues were primarily present in the \fs code, which is not surprising considering the participants' experience.
